---
date: '2022-06-23'
output: pdf_document
---

# **EDA LAII**
# _____________________________
## By                          
## Chetna Pathak(1NT19IS045)   
## Abhiruchi Verma(1NT19IS002) 
# _____________________________
\vspace{12pt}

### Basketball Database
### https://www.kaggle.com/wyattowalsh/basketball

### github link
### https://github.com/Chetna045/EDA-LAII-basketballdatabse

\vspace{12pt}
# Commands

# ______________________________________________________________________________

## checking for installed packages
```{r}
installed.packages("dplyr")
```
## installing necessary packages

```{r}
#install.packages("DBI")
#install.packages("dplyr")
```
## loading packages

```{r}
library(DBI)
library(dplyr)
```
## getting help using command
```{r}
help("DBI-package")
```
## Making connection with sqlite database

```{r}
setwd("C:/Users/Hp/Downloads/archive")
con <- dbConnect(RSQLite::SQLite(), "basketball.sqlite")
```

## Displaying all tables of database Basketball

```{r}
dbListTables(con)
```

## basic commands of R(searching ,loading and detaching a package)
```{r}
search()
#install.packages("blob")
library(blob)
search()
detach("package:blob")
```
##listing files and directories in working directory
```{r}
dir()
# hidden files  too
dir(all.files = TRUE)

```
##listing data variables
```{r}
ls()
ls(pattern="ga")
# all data variables starting with g
ls(pattern="^g")
# all data variables ending with s
ls(pattern = "s$")
# all data variables having a letter  in between a and e
ls(pattern = "a.e")

```
## making reference to tables in database

```{r}
game<-tbl(con,"Game")
draft<-tbl(con,"Draft")
draft_combine<-tbl(con,"Draft_Combine")
game_inactive_players<-tbl(con,"Game_Inactive_Players")
game_officials<-tbl(con,"Game_Officials")
news<-tbl(con,"News")
news_missing<-tbl(con,"News_Missing")
player<-tbl(con,"Player")
player_attributes<-tbl(con,"Player_Attributes")
player_bios<-tbl(con,"Player_Bios")
player_photos<-tbl(con,"Player_Photos")
player_salary<-tbl(con,"Player_Salary")
team<-tbl(con,"Team")
team_attributes<-tbl(con,"Team_Attributes")
team_history<-tbl(con,"Team_History")
team_salary<-tbl(con,"Team_Salary")



```
## displaying table team
```{r}
team
```
## viewing team column of database basketball

```{r}
View(team)
```
##  team table  dimension
```{r}
dim(team)

```
## team column starting data
```{r}
head(team)
```
## team  column summary
```{r}
summary(team)
```
## team column structure 
```{r}
str(team)
```
## team coloumn column names
```{r}
names(team)
colnames(team)
```
## team table row names
```{r}
row.names(team)
```
## team column city
```{r}
team$city
```
## type of team
```{r}
typeof(team)
```
```{r}
tt<- team %>% select("id","full_name") 
tt
```
## converting team table into a dataframe
```{r}
team.data.frame<-dbGetQuery(con,"SELECT * From Team")
team.data.frame
team.data.frame[1][0]
summary(team.data.frame)
```
## commands on dataframe
```{r}
team.data.frame[1]
team.data.frame[["city"]]
team.data.frame$year_founded
# adding new row
new_row_df<-rbind(team.data.frame,c(1610612767,"Chicago Super Kings","CHI","Kings","Chicago" ,"Illinois",2022))
new_row_df
nrow(new_row_df)
#removing rows
newr.team<-new_row_df[-c(31),]
newr.team
# adding a column
vec<-rep(c(6,4),15)
new_col_df<-cbind(team.data.frame,Match_hosted=(vec))
new_col_df
ncol(new_col_df)

#removing columns
newc.team<-new_col_df[,-c(8)]
newc.team
#length of data frame 
length(team.data.frame)

```
## mutate dataframe  (using pipline operator)
```{r}
library(dplyr)
mutated.team<-team.data.frame %>% mutate (new_col=vec<-rep(c(3,9),15))
team.data.frame
```
## deleting column from dataframe (using pipline operator)
```{r}
mutated.team %>% select(-new_col)
```
## renaming column from dataframe (using pipline operator)
```{r}
mutated.team %>% rename(identity_no.=id)
```
## reordering column from dataframe (using pipline operator)
```{r}
mutated.team %>% select(abbreviation,everything())
```
## renaming column from dataframe (using pipline operator)
```{r}
mutated.team %>% rename(identity_no.=id)
```
## getting subset of data(using pipline operator)
```{r}
table(mutated.team$full_name)
mutated.team %>% filter(state=="California")
mutated.team %>%filter(state=="New York") %>% select(id,full_name,state,year_founded)
```

## saving team details to an csv file and reading it

```{r}
write.csv(team.data.frame,file="team.csv")
read.csv("C:/Users/Hp/Downloads/archive/team.csv")
```

## converting dataframe as list
```{r}
team.list=as.list(team.data.frame);
team.list
```
## basic commands on list
```{r}
team.list$state
# naming each element of list
names(team.list)<-c("identity_no.", "Fname","abbr","petname","city","state","founding_year")
team.list
# accessing elements of list
team.list[1]
team.list[5]
# adding new element to list
team.list[8]<-"New_Element"
team.list
# deleting element from list
team.list[8]<-NULL
team.list
```
## converting list to vectors
```{r}
v1<-unlist(team.list$id);
v1
```
## sort and rank
```{r}
sort(v1)
rank(v1)

```
## converting dataframe as Matrix
```{r}
team.mat=as.matrix(team.data.frame);
team.mat
```

## converting "state" column of "mutated.team" dataframe to factor
```{r}

mutated.team$state=as.factor(mutated.team$state)
str(mutated.team$state)
```
## grouping by state and mutating by adding new coloumn "new"(since state has common values)
```{r}
mutated.team %>% group_by(state)%>%mutate(new<-mean(new_col))

```
## grouping by state and summarising
```{r}
mutated.team %>% group_by(state)%>%summarise(avg=mean(new_col))

```
## converting Player table into a dataframe
```{r}
draft.df<-dbGetQuery(con,"SELECT * From draft")
draft.df[1:40,]
draft.df[1][0]
summary(draft.df)
str(draft.df)
```
## mean,median,standard deviation &mode of data based of on no. of times picked
```{r}
mean(draft.df$ numberRoundPick, na.rm = TRUE)
median(draft.df$numberRoundPick, na.rm = TRUE)
mode(draft.df$numberRoundPick)
sd(draft.df$numberRoundPick)
fivenum(draft.df$numberRoundPick)
log(draft.df$numberRoundPick)
#20%quantile
quantile(draft.df$numberRoundPick,0.2)
max(draft.df$numberRoundPick)
min(draft.df$numberRoundPick)
cumsum(draft.df$numberRoundPick)
cummax(draft.df$numberRoundPick)
cummin(draft.df$numberRoundPick)
cumprod(draft.df$numberRoundPick)
seq(along=draft.df$numberRoundPick)
seq(1,14,16)
draft.ls=as.list(draft.df)
lapply(draft.ls,mean)


```

## barplot 
```{r}
draft.mat=as.matrix(draft.df)
barplot(draft.mat[,1:4])

```







## plots
```{r}
plot(draft.df[1:80,4],type = "l")
plot(draft.df[1:80,2],type = "l")
plot(draft.df[1:80,3],type = "l")
plot(draft.df[1:80,1],type = "l")
plot(draft.df[1:80,4],type = "l")
lines(draft.df[1:80,3],col="red",type = "l")
lines(draft.df[1:80,2],col="blue",type = "l")
```






## plotting a bargraph using ggplot
```{r}
library(ggplot2)
ggplot(draft.df,aes(x=numberRound,y=numberRoundPick))+geom_col()
```




## using ggplot plotting a bar graph with fill 
```{r}
ggplot(draft.df,aes(x=numberRound,y=numberRoundPick,fill=numberPickOverall))+geom_col()
```





## using ggplot plotting a line graph
```{r}
ggplot(draft.df,aes(x=numberRound,y=numberRoundPick))+geom_line()
```






## using ggplot plotting a point graph
```{r}
ggplot(draft.df,aes(x=numberRound,y=numberRoundPick))+geom_point()
```





## using ggplot plotting a boxplot
```{r}
ggplot(draft.df,aes(x=numberRound,y=numberRoundPick))+geom_boxplot()

```






## Histogram 
```{r}
hist(draft.df$yearDraft)

```





## boxplot
```{r}
boxplot(draft.df$yearDraft)

```





## plotting a ling graph with points
```{r}
 plot(draft.df[1:80,4],type="l")
points(draft.df[1:80,3],col="blue")
```






## pieChart
```{r}
pie(draft.df[1:30,1],lables="Draft year")
```





## ScatterPlot
```{r}
library(scatterplot3d)
scatterplot3d(draft.df[1:500,2],draft.df[1:500,3],draft.df[1:500,4],main="3d scatterplot")

```





##scatterPlot matrices
```{r}
col1=draft.df[1:40,2]
col2=draft.df[1:40,3]
sdf=data.frame(col1,col2)
sdf
```





## vioplot
```{r}
library(vioplot)
vioplot(sdf)

```

